### 2025-05-05 evaluating-prediction-accuracy.qmd
20250505 - remove subject indexing for now

It is preferable to examine predictive $R^2$ using new data that the model was not trained on—i.e., cross-validation, either in an independent sample (i.e., external cross-validation) or in a hold-out sample (i.e., internal cross-validation on test data).\index{predictive $R^2$}\index{cross-validation}

For example, here is an example of estimating predictive $R^2$ 10-fold cross-validation using the `caret` package [@R-caret].\index{predictive $R^2$}\index{cross-validation}

>>>>

It is preferable to examine predictive $R^2$ using new data that the model was not trained on—i.e., cross-validation, either in an independent sample (i.e., external cross-validation) or in a hold-out sample (i.e., internal cross-validation on test data).

For example, here is an example of estimating predictive $R^2$ 10-fold cross-validation using the `caret` package [@R-caret].
